### 2024-05-28 Data/AnalysisData/codebook_plot_data_structure_data.Rmd
revised the entire text to the main article form. Added a new figure, removed some tables and analyses, appendiced some analyses.

---
title: "Codebook created on 2024-03-18 at 2024-03-18 14:12:52.006764"
output: github_document
---

@@

## Dataset description
The data contains 19 cases and 3 variables.

@@

```{r}
summaries <- read.csv("codebook_cfa_results.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2024-05-22 at 2024-05-22 10:01:49.511004"
output: github_document
---

@@

## Dataset description
The data contains 112 cases and 91 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_data_structure_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2024-05-28 Data/Data_package_description.Rmd
revised the entire text to the main article form. Added a new figure, removed some tables and analyses, appendiced some analyses.

*Explanation*: The information in this dataset was used for analyses relating to QMP ratios among original articles and replication studies. It additionally contains peripheral information about the articles and study in it that were used throughout the analyses and for descriptives.

@@

>>>>

*Explanation*: The information in this dataset was used for analyses relating to QMP ratios among original articles and replication studies. It additionally contains peripheral information about the articles and study in it that were used throughout the analyses and for descriptives. Questions related to modification had 'no modification' as an additional answer option, in case that specific aspect of the measure was explicitly not modified, but might possibly have been applicable, because it was a relevant aspect albeit unmodified. But these operated equivalently to the Not applicable response with respect to the calculation of the QMP ratio. They are included here for future reference.

@@

### plot_data_structure_data.csv

*Explanation*: Contain all of the data from the data_h4.csv filtered based on having a unique title (that was not due to a typo or copying error) to extract the individual studies and replication rather than individual measures into a dataset. Furthermore, the total count of measures for each study or replication was added to this dataset.

### 2024-05-28 Scripts/Manuscript/AppendixScripts/Appendix_pre-reg_analyses.Rmd
revised the entire text to the main article form. Added a new figure, removed some tables and analyses, appendiced some analyses.

@@

The model was the same as that used for the main test of hypothesis 6 (see formula \@ref(eq:H6Main)), only now QMP ratios for each of the five categories were used one at a time for each unique combination of original article and replication protocol QMP.

>>>>

## Intraclasscorelation assessment for within measure variation in reliability

### Pre-registration Analysis Justification & Reason for Omission from Article
Reliabilities could be calculated from the replication datasets. On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of them could be assessed. In order to separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the lmer function from the lme4 package [@R-lme4] t.

```{r Hypothesis2Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)

The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets. However, at the time of pre-registering we did not know of any formal test for the significance of within group variance after controlling for between group variance. Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs. between variability.

```{r ICCCalculations, include = FALSE}
# Variances
within_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha), "sc")^2
between_group_variance_alpha <- attr(VarCorr(H2_test_result_alpha)$g, "stddev")^2

# ICC
ICC_alpha <- between_group_variance_alpha / (within_group_variance_alpha + between_group_variance_alpha)

This analysis was omitted from the article because it did not link well enough to hypothesis 2. THe test results also do not give use a very informative representations of variance in reliability in the data for us to draw further inferences from. For instance, it assumes that we should observe large differences in reliabilities between measures for this to provide an accurate test of whether or not the variance within measures is large or not.

### Results
The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively. The resulting ICC, was approximately `r apa_num(ICC_alpha, digits = 3)`. This suggests that variance was larger between replication sets than within. These results are generally in line with hypothesis 2. However, this statistic does not necessarily gives a test of hypothesis 2, as outlined above.

@@

The model was the same as that used for the main test of hypothesis 6, only now QMP ratios for each of the five categories were used one at a time for each unique combination of original article and replication protocol QMP.
